\chapter{Procedure}
\section{Goals}
The goal with this Usability Testing is to test our overall logic and design of the application. This to test the product concept and reveal and catch potential confusing experiences with the product in an early stage. The test participants will give the Company indications of how the navigation of the application feels and where improvements can be made.
\section{Methodology}
The participants will take part in the usability test remote by getting a link to our prototype and screen share the whole test process. The test leader will ask the participants to do some tasks or give the participants a scenario to complete. The participant is asked to think out loud when the task/scenario is conducted. \\

\noindent\textbf{The tasks/scenarios/questions were:}

\begin{enumerate}
\item Finish the guide that is displayed to get an understanding of the application. Did you find it informative?  
\item You want to change your password. How will you proceed? 
\item You want to enter a new value for your blood sugar level. How do you proceed?
\item You filled in that you were out walking this morning, but now you realized that you entered the wrong value. You want to change your previously entered value to the correct value. How do you proceed?
\item You have just disagreed with your cousin Amanda, who you previously gave permission in the app to see all your medical data you register in the app. But now you do not want Amanda to have access to this anymore. How do you proceed? 
\item You want to see your goals related to diabetes. How do you proceed?
\item You want to see all your previously registered activity values. How do you proceed? 
\item You want to see all your previously achieved achievements. How do you proceed?
\item You want to read more about the displayed tree and understand what it is. How do you proceed?
\item You have understood that the trees in the application are a form of gamification, how do you go about reducing the degree of gamification in the application?
\item You want to follow up your progress in one of your set goals "Lose 5 kg". How do you proceed?
\item You want to re-do the initial guide that was displayed when you first entered the application. How do you proceed? \\
\end{enumerate} 

\noindent Upon completion of the tasks, the participants were asked to fill in a form with the questions presented below. Participants answered through a likert scale from one to five where one means strongly disagree and five means strongly agree. This scale was then used for measuring the SUS of the application. \\ 
\begin{enumerate}
\item I think that I would like to use this system frequently. 
\item I found the system unnecessarily complex. 
\item I thought the system was easy to use. 
\item I think that I would need the support of a technical person to be able to use this system. 
\item I found the various functions in this system were well integrated. 
\item I thought there was too much inconsistency in this system. 
\item I would imagine that most people would learn to use this system very quickly. 
\item I found the system very cumbersome to use. 
\item I felt very confident using the system. 
\item I needed to learn a lot of things before I could get going with this system. \\ 
\end{enumerate}
The participants will also after the test be asked some post-test questions to gain a deeper understanding about how they felt about the product overall. \\ 

\noindent\textbf{These questions are:} 
\begin{itemize}
\item What's your spontaneous impression of the application?
\item What do you like most about the application?
\item What do you dislike the most about the application?
\item If you had to change one attribute in the design, what would you change?
\item Did the navigation between different pages in the application feel natural?
\item Was any task/scenario difficult to perform? why?
\item Do you think that the English language of the application might have had an impact on your test, and if so how? 
\item What do you think Streaks mean? \\
\end{itemize}
\noindent Since the test leaders will conduct the tests alone due to some resource restraints each test will be recorded to make sure that the report includes everything. Lostness (amount of clicks and on what nodes), current thinking out loud and answers to questions will therefore be transcribed from a recording and be rewritten into this report. 






