\chapter{Introduction}

\section{Executive summary}
The participants did most of the tasks/scenarios with the minimum amount of clicks needed to complete a task/scenario which indicated that the overall design of the application is understandable and easy to understand. Overall the participants felt that they like the design and that it's clean, easy and contains just the right amount of information. The participants emphasized the importance of a minimalistic design in application for these contexts and believed that it was achieved with this application. Some of the participants had a few tasks which took more clicks to complete due to misunderstanding of the task or, most often, due to the icons. All of the participants believed that the icons for the Home- and Profile-page were clear and optimal but most of them also thought that the History- and Goals-icons could be improved. These improvements could be done by either changing icons or implementing an initial guide that pops up during the first launch of the application. None of the  participants had a perfectly clear understanding of what Streaks are. However, some of the participants had a good understanding and compared it to other applications such as Duolingo. One of the participants did not recognize the word or the concept from before.,

\section{Participants}
\begin{itemize}
    \item Participant 1: Female, age 33
    \item Participant 2: Female, age 38
    \item Participant 3: Male, age 55
    \item Participant 4: Male, age 56
    \item Participant 5: Male, age 25
\end{itemize}